\textbf{Providing Access Control and Copy-on-Write for Content Distribution Network Assets}

### 2016-04-06 tex/paper.tex
Added explanations and changed to description latex type

\subsection{Elements of the Model}
In this section we show the elements of the model, identify the different sets and explain how they
should be interpreted. This is done in the same way as in \textit{Secure Computer Systems: Mathematical
Foundations}~\cite{BLP1} by Bell \& LaPadula.

@@

\hfill \par \textbf{Content} \\
Content is metadata about a file and is stored in a container, it is a form of virtual file.  The
content can refer to for example an image, video or binary blob.\\

\par \textbf{Project} \\
A project is what is created to contain all content and containers related to a real project. Files
and metadata can only be changed within a project and the system can contain several projects 
that have their virtual content and containers completely disjoint.\\

\par \textbf{Container} \\
A container is a virtual folder within a project which can contain content and other containers.\\

\par \textbf{Snapshot} \\
A snapshot is a read-only container from the state which the container was in when the snapshot
was created.  A snapshot can not be updated and can only be deleted from the root of the snapshot.
Snapshots are by default stored as siblings to the container which they were made from, but they can
be contained by any container.\\

\par \textbf{File} \\
A file refers to an actual physical file. Files are stored in the database to make backup,
deployment and migration easier.\\

\par \textbf{User} \\
A user is the structure that handles people who have been granted access to the system. Access to
the system is handled by a separate service, like LDAP.\\

@@

\subsubsection{Runtime Complexity of Operations} \label{sec:run_time}
The runtime complexities of the operations in this section are quite intuitive, that is why they 
are only explained, and not proven to fulfill the complexities which are claimed. 
%To prove them, methods like the master theorem~\cite{ALGORITHMS} or \dots could be used.

>>>>

\subsection{Sets and Elements of the Model}\label{sec:elements}
In this section we show the elements of the model, identify the different sets and explain how they
should be interpreted. This is done in the same way as in \textit{Secure Computer Systems: Mathematical
Foundations}~\cite{BLP1} by Bell \& LaPadula.

@@

All the entities in Figure~\ref{fig:relation} is described in Section~\ref{sec:elements}, except for
projects, which is explained below. \\
\vspace{0.5em}

A \textbf{Project} is what is created to contain all content and containers related to a real project. Files
and metadata can only be changed within a project and the system can contain several projects 
that have their own virtual content and containers completely disjoint from the other projects.\\

@@

\subsubsection{Entities of the Implementation}
This section explains the different types of entities, and their interaction, that are handled by
Perius. They are explained similarly to how they are explained for the model in
Section~\ref{sec:elements}, but with more implementation specific details.

\begin{description}
\item[Content] \hfill \\
Content is metadata about a file and is stored in a container, it is a form of virtual file.  The
content can refer to for example an image, video or binary blob.\\

\item[Project] \hfill \\
A project is what is created to contain all content and containers related to a real project. Files
and metadata can only be changed within a project and the system can contain several projects 
that have their virtual content and containers completely disjoint. Each project is handled as a
separate database in MongoDB.\\

\item[Container] \hfill \\
A container is a virtual folder within a project which can contain content and other containers.\\

\item[Snapshot] \hfill \\
A snapshot is a read-only container from the state which the container was in when the snapshot
was created.  A snapshot can not be updated and can only be deleted from the root of the snapshot.
Snapshots are by default stored as siblings to the container which they were made from, but they can
be contained by any container.\\

\item[File] \hfill \\
A file refers to an actual physical file. Files are stored in the database to make backup,
deployment and migration easier.\\

\item[User] \hfill \\
A user is the structure that handles people who have been granted access to the system. Access to
the system is handled by a separate service, like LDAP.\\

\end{description}
\subsubsection{Runtime Complexity of Operations} \label{sec:run_time}
The runtime complexities of the operations in this section are quite intuitive, that is why they 
are only explained, and not proven to fulfil the complexities which are claimed. 
%To prove them, methods like the master theorem~\cite{ALGORITHMS} or \dots could be used.
